---
title: "Inference for synthetic control methods: the scinference package"
author: "Victor Chernozhukov, Kaspar Wuthrich, Yinchu Zhu"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Inference for synthetic control methods: the scinference package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The package scinference implements the inference methods for synthetic control and related methods proposed in the following two papers:

"An Exact and Robust Conformal Inference Method for Counterfactual and Synthetic Controls" written by V. Chernozhukov, K. Wuthrich, and Y. Zhu (2020). The paper is available here: https://arxiv.org/abs/1712.09089. 

"Practical and robust t-test based inference for synthetic control and related methods" written by V. Chernozhukov, K. Wuthrich, and Y. Zhu (2020). The paper is available here: https://arxiv.org/abs/1812.10820. 

# Overview

The package can be used to make inferences in settings with one treated unit and $J\ge 1$ control units, where the treated unit is untreated for the first $T_0$ time periods and treated for the remaining $T_1$ periods.

## Conformal inference
The package computes p-values for the null hypothesis that $H_0:(\theta_{T_0+1},\dots,\theta_{T_0+T_1})=(\theta^0_{T_0+1},\dots,\theta^0_{T_0+T_1})$, where $(\theta_{T_0+1},\dots,\theta_{T_0+T_1})$ is the vector of treatment effects in the post-treatment period. The p-values can be computed using moving block and iid permutations. If ci=TRUE, the package also computes pointwise $(1-\alpha)$ confidence intervals for $\theta_t$ for all $T_0+1\le t \le T_0+T_1$.

## T-test

The package computes the debiased estimator of the ATT over time, $T_1^{-1}\sum_{t=T_0+1}^{T_0+T_1}\theta_t$, including $(1-\alpha)$ confidence intervals. Note that this method requires $T_1$ to be large.

## Estimators of the counterfactuals
The package implements three different estimators of the counterfactuals: difference-in-differences, canonical synthetic control, constrained Lasso. Note that the implementation of synthetic control uses only pre-treatment outcomes as predictors and does not accommodate additional covariates. Moreover, the t-test is currently only available for difference-in-differences and synthetic control.

# Examples

The package is available for download on github. 
```{r install}
library(scinference)
```
## Conformal inference

We start by illustrating conformal inference using some simulated data. We consider a setup with $J=50$, $T_0=50$, and $T_1=5$. The control data as generated as iid normal; the outcome equals a weighted average of the contemporaneous control outcomes with sparse weights $(1/3,1/3,1/3,0,\dots,0)$. The treatment effect is constant and equal to $2$ for all periods.
```{r setup}
set.seed(12345)

J   <- 50
T0  <- 50 
T1  <- 5

w       <- rep(0,J)
w[1:3]  <- 1/3
Y0      <- matrix(rnorm((T0+T1)*J),(T0+T1),J)
Y1      <- Y0 %*% w + rnorm(T0+T1)

Y1[(T0+1):(T0+T1)] <- Y1[(T0+1):(T0+T1)] + 2
```
We start by testing the null hypothesis $H_0:\theta=(4,4,4,4,4)'$. We compare the results for all three estimation methods and for both types of permutations. By default, the p-value based on the iid permutations is computed using 5000 randomly-drawn permutations.
```{r null}
scinference(Y1,Y0,T1=T1,T0=T0,theta0=4,estimation_method="sc",permutation_method="mb")$p_val
scinference(Y1,Y0,T1=T1,T0=T0,theta0=4,estimation_method="did",permutation_method="mb")$p_val
scinference(Y1,Y0,T1=T1,T0=T0,theta0=4,estimation_method="classo",permutation_method="mb")$p_val

scinference(Y1,Y0,T1=T1,T0=T0,theta0=4,estimation_method="did",permutation_method="iid")$p_val
scinference(Y1,Y0,T1=T1,T0=T0,theta0=4,estimation_method="sc",permutation_method="iid")$p_val
scinference(Y1,Y0,T1=T1,T0=T0,theta0=4,estimation_method="classo",permutation_method="iid")$p_val
```
Next, we compute pointwise confidence intervals using the synthetic control method. This requires specifying a grid (see Algorithm 1 in the corresponding paper).
```{r ci}

obj <- scinference(Y1,Y0,T1=T1,T0=T0,estimation_method="sc",ci=TRUE,ci_grid=seq(-2,8,0.1))

plot(1, ylab="", xlab="Time", main="90% pointwise CIs",xlim = c(1,5), ylim=c(-1,7), type="n")
lines(1:5, obj$lb, lwd = 2)
lines(1:5, obj$ub, lwd = 2)
abline(h=0,col="darkgrey", lwd=1)
```

## T-test
We start by generating some data. Note that the t-test requires a large number of post treatment periods. We use a similar DGP as before.
```{r data_ttest}
set.seed(12345)

J   <- 30
T0  <- 30 
T1  <- 30

w       <- rep(0,J)
w[1:3]  <- 1/3
Y0      <- matrix(rnorm((T0+T1)*J),(T0+T1),J)
Y1      <- Y0 %*% w + rnorm(T0+T1)

Y1[(T0+1):(T0+T1)] <- Y1[(T0+1):(T0+T1)] + 2
```
We apply the t-test with synthetic control and $K\in \{2,3\}$ to estimate the ATT over time and 90% confidence intervals.
```{r ttest}
ttest_K2 <- scinference(Y1,Y0,T1=T1,T0=T0,inference_method="ttest",K=2)
ttest_K2$att 
ttest_K2$se 
ttest_K2$lb
ttest_K2$ub
ttest_K3 <- scinference(Y1,Y0,T1=T1,T0=T0,inference_method="ttest",K=3)
ttest_K2$se 
ttest_K3$att 
ttest_K3$lb
ttest_K3$ub
```



